The ChEMBL database as Linked Open Data

### 2012-07-10 article.tex
Updated DS screenshot and caption.

\begin{figure*}[!ht]
		\begin{center}
		\includegraphics[width=16cm]{bioclipse-ds.png}
		\newline
		\caption[wee]{Screnshot from Bioclipse Decision Support with results from a ChemSpider + ChEMBL-RDF search. The top middle canvas contains the query structure, the top right canvas shows the near neighbors in ChemSpider (via a similarStructure search), the lower right shows the chemical structure for the selected compound in the top right canvas, and the lower center canvas shows the found interactions for this compound.}
	\label{fig:bioclipse-ds}
		\end{center}
\end{figure*}

>>>>

\begin{figure*}[!ht]
		\begin{center}
		\includegraphics[width=15cm]{bioclipse-ds.png}
		\newline
		\caption[wee]{Screnshot from Bioclipse Decision Support with results from a ChemSpider + ChEMBL-RDF search. The top left canvas contains the query structure, in this case the drug Carbamezapine, the top right canvas shows the near neighbors in ChemSpider (via a similarStructure search) that contain ChEMBL-RDF data, the lower right shows the chemical structure for the selected compound in the top right canvas, and the lower left canvas shows the found interactions for this compound using ChEMBL-RDF.}
	\label{fig:bioclipse-ds}
		\end{center}
\end{figure*}
